A matrix-free approach for finite-strain hyperelastic problems using geometric multigrid

### 2018-09-04 doc/large_strain.tex
more edits

  \begin{abstract}
    Solution of source problems on modern computer architectures is typically memory bound.
    Loading matrix elements is significantly slower than performing the arithmetic operations when solving the problem.
    In order to improve the performance of the iterative solver, the so-called matrix-free methods are
    widely adopted in fluid mechanics community, where the matrix vector products are formed on-the-fly.

    In this work we advance the application of matrix-free approaches to problems in solid mechanics.
    We propose and numerically investigate different implementations of the finite-strain hyper-elastic tangent operator.
    In order to improve the convergence of iterative solvers, we also propose a way to construct level tangent operators
    and employ them to define a geometric multigrid preconditioner.
    Our implementation employs MPI and Intel Threading Building Blocks parallelization and SIMD vectorization.
    The performance of the matrix-free operator and the geometric multigrid preconditioner is compared to the matrix-based counterparts on the representative numerical example of heterogeneous hyper-elastic material in two and three dimensions.
  \end{abstract}

>>>>

  \begin{abstract}
    The performance of finite element solvers on modern computer architectures is typically memory bound.
    The main cause for this is that loading matrix elements is significantly slower than performing the arithmetic operations when solving the problem.
    In order to improve the performance of the iterative solver, so-called matrix-free methods are
    widely adopted in fluid mechanics community, where the matrix vector products are formed on-the-fly.

    In this work, we advance the application of matrix-free approaches to problems in solid mechanics.
    We propose and numerically investigate different implementations of the finite-strain hyper-elastic tangent operator.
    In order to improve the convergence of iterative solvers, we also propose a way to construct level tangent operators
    and employ them to define a geometric multigrid preconditioner.
    Our implementation employs MPI and Intel Threading Building Blocks parallelization and SIMD vectorization.
    The performance of the matrix-free operator and the geometric multigrid preconditioner is compared to the matrix-based counterparts on the representative numerical example of heterogeneous hyper-elastic material in two and three dimensions.
  \end{abstract}
